Subsegmental language detection in Celtic language text

### 2014-05-08 codeswitch-cltw-2014/codeswitch.tex
update
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52621 72bbbca6-d526-0410-a7d9-f06f51895060

\title{Instructions for COLING-2014 Proceedings}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

>>>>

\title{Subsegmental language detection in Celtic language text}

\author{Akshay \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Francis M. Tyers \\
  Giellatekno / CLEAR \\
  UiT Norgga \'arktala\v{s} universitehta  \\
  9017 Romsa (Norway) \\
  {\tt francis.tyers@uit.no} \\}
